Dismal Code: Studying the Evolution of Security Vulnerabilities

### 2013-01-19 docs/msr.tex
more content

One of the most common approaches to identify software vulnerabilities is
{\it static analysis}~\cite{CW07}. This kind of analysis is performed by automated tools
either on the program's source or object code and without actually executing
it. For our research we used {\it FindBugs},\footnote{\url{http://findbugs.sourceforge.net/}}
an effective static analysis tool that has already been used in
research~\cite{AP10, HP07}. Specifically, we ran FindBugs on all the project
versions of all the projects that exist in the Maven repoistory (280GB of
data). Then we observed the changes that involved the security bugs per project
version.

>>>>

One of the most common approaches to identify software vulnerabilities is
{\it static analysis}~\cite{CW07}. This kind of analysis is performed by automated tools
either on the program's source or object code and without actually executing
it. For our research we used {\it FindBugs},\footnote{\url{http://findbugs.sourceforge.net/}}
an effective static analysis tool that has already been used in
research~\cite{AP10, HP07}. Specifically, we ran FindBugs on all the project
versions of all the projects that exist in the Maven repoistory (265GB of
data). Then we observed the changes that involved the security bugs and their
characteristics, per project version.

We chose to focus our study on the security-related bugs rather than other
software bugs for a number of reasons.
